Cross-national analyses require additional controls to account for the non-independence of nations

### 2023-08-08 manuscript.Rmd
add zenodo doi citation
final author changes

author: 
  - name          : "Scott Claessens"
    affiliation   : "1"
  - name          : "Thanos Kyritsis"
    affiliation   : "1"
  - name          : "Quentin D. Atkinson"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "\\footnotesize School of Psychology, University of Auckland, Auckland, New Zealand"
  - id            : "2"
    institution   : "\\footnotesize School of Anthropology and Museum Ethnography, University of Oxford, Oxford, United Kingdom"

authornote: "Correspondence concerning this article should be addressed to Scott Claessens (scott.claessens@gmail.com) and Quentin D. Atkinson (q.atkinson@auckland.ac.nz), Floor 2, Building 302, 23 Symonds Street, Auckland, 1010, New Zealand. \\newline \\indent The authors made the following contributions. Scott Claessens: Conceptualization, Data curation, Formal analysis, Investigation, Software, Visualization, Writing - original draft, Writing - review & editing; Thanos Kyritsis: Data curation, Writing - review & editing; Quentin D. Atkinson: Conceptualization, Data curation, Funding acquisition, Supervision, Writing - review & editing."

@@

@@

Given that economic development and cultural values show evidence of geographic and cultural phylogenetic signal, have cross-national analyses sufficiently accounted for this non-independence? To assess this, we searched the published literature for articles that combined the search terms "economic development" or "values" with the search terms "cross-national", "cross-cultural", or "cross-country". We removed articles that did not report original research, were not relevant to economic development or cultural values, or did not report at least one cross-national analysis. We then retained the 100 articles (50 for economic development, 50 for cultural values) with the highest annual rate of citations (see Supplementary Data). For each of these highly-cited articles, we exhaustively recorded every cross-national analysis reported in the main text (n = `r printnum(as.numeric(nrow(review)), digits = 0)`), identifying in each case whether or not the analysis attempted to control for spatial, cultural, or any other form of non-independence between nations (see Methods for detailed search criteria and coding decisions).

@@

We exported two searches from Web of Science (https://www.webofknowledge.com/) on 27^th^ September 2021, restricting our searches to articles published between 1900 and 2018. The first search was for the terms "economic development" AND ("cross-national" OR "cross-cultural" OR "cross-country"), which returned 965 articles. The second search was for the terms "values" AND ("cross-national" OR "cross-cultural" OR "cross-country"), which returned 6806 articles. Once exported, we ordered the articles by descending number of citations per year since initial publication, using citation counts reported by Web of Science.

We then coded each article, in order, for inclusion in our review. Articles were only included if: (1) they were judged to be relevant to economic development or cultural values; (2) they were an original empirical research article; and (3) they contained at least one analysis with national-level outcome or predictor variables. We stopped when we had included 50 articles for the economic development review and 50 articles for the cultural values review.

@@

All data and code are accessible on GitHub (https://github.com/ScottClaessens/crossNationalCorrelations). We used the targets R package[@Landau2021] to create a reproducible data analysis pipeline and the papaja R package[@Aust2020] to reproducibly generate the manuscript.

@@

Ethical approval was not required for the study as we analysed only secondary and simulated data. We did not apply for ethical approval through an ethics board.

@@

All data can be found on GitHub (https://github.com/ScottClaessens/crossNationalCorrelations). Data on human development were retrieved from the United Nations Development Programme (https://hdr.undp.org/en/content/download-data). Data on GDP per capita, annual GDP per capita growth, and the Gini coefficient were retrieved from the World Bank (https://data.worldbank.org/). Data on traditional vs. secular values and survival vs. self-expression values were retrieved from the World Values Survey (https://www.worldvaluessurvey.org/wvs.jsp). Data on cultural tightness were retrieved from the OSF repository for Gelfand et al. 2021 (https://osf.io/47pe8/). The review data generated in this study are provided in the Supplementary Data file. All other datasets (e.g., for replications) were retrieved from tables and supplementary tables directly from papers cited in the main text[@Adamczyk2009;@Alesina2013;@Beck2003;@Beck2005;@Bockstette2002;@Easterly2003;@Easterly2007;@Fincher2008;@Gelfand2011;@Inglehart2000;@Knack1997;@Skidmore2002] - these datasets can be found in our GitHub repository.

@@

All code to reproduce the statistical analyses in this manuscript can be found on GitHub (https://github.com/ScottClaessens/crossNationalCorrelations).

>>>>

author: 
  - name          : "Scott Claessens"
    affiliation   : "1*"
  - name          : "Thanos Kyritsis"
    affiliation   : "1"
  - name          : "Quentin D. Atkinson"
    affiliation   : "1,2*"

affiliation:
  - id            : "1"
    institution   : "\\footnotesize School of Psychology, University of Auckland, Auckland, New Zealand"
  - id            : "2"
    institution   : "\\footnotesize School of Anthropology and Museum Ethnography, University of Oxford, Oxford, United Kingdom \\newline *email: scott.claessens@gmail.com; q.atkinson@auckland.ac.nz"

@@

# Introduction

@@

Given that economic development and cultural values show evidence of geographic and cultural phylogenetic signal, have cross-national analyses sufficiently accounted for this non-independence? To assess this, we searched the published literature for articles that combined the search terms "economic development" or "values" with the search terms "cross-national", "cross-cultural", or "cross-country". We removed articles that did not report original research, were not relevant to economic development or cultural values, or did not report at least one cross-national analysis. We then retained the 100 articles (50 for economic development, 50 for cultural values) with the highest annual rate of citations (see Supplementary Data 1). For each of these highly-cited articles, we exhaustively recorded every cross-national analysis reported in the main text (n = `r printnum(as.numeric(nrow(review)), digits = 0)`), identifying in each case whether or not the analysis attempted to control for spatial, cultural, or any other form of non-independence between nations (see Methods for detailed search criteria and coding decisions).

@@

We exported two searches from Web of Science (https://www.webofknowledge.com/) on 27^th^ September 2021, restricting our searches to articles published between 1900 and 2018. The first search was for the terms "economic development" AND ("cross-national" OR "cross-cultural" OR "cross-country"), which returned 965 articles. The second search was for the terms "values" AND ("cross-national" OR "cross-cultural" OR "cross-country"), which returned 6806 articles. As this was not a formal systematic literature review, we did not follow PRISMA[@Page2021] guidelines for systematic literature reviews.

Once exported, we ordered the articles by descending number of citations per year since initial publication, using citation counts reported by Web of Science. We then coded each article, in order, for inclusion in our review. Articles were only included if: (1) they were judged to be relevant to economic development or cultural values; (2) they were an original empirical research article; and (3) they contained at least one analysis with national-level outcome or predictor variables. We stopped when we had included 50 articles for the economic development review and 50 articles for the cultural values review.

@@

All data and code are accessible on GitHub[@github]. We used the targets R package[@Landau2021] to create a reproducible data analysis pipeline and the papaja R package[@Aust2020] to reproducibly generate the manuscript.

@@

We did not apply for ethical approval through an ethics board as we analysed only publicly available and simulated data in this study.

@@

All data to reproduce the statistical analyses in this manuscript can be found on GitHub[@github]. Data on human development were retrieved from the United Nations Development Programme (https://hdr.undp.org/en/content/download-data). Data on GDP per capita, annual GDP per capita growth, and the Gini coefficient were retrieved from the World Bank (https://data.worldbank.org/). Data on traditional vs. secular values and survival vs. self-expression values were retrieved from the World Values Survey (https://www.worldvaluessurvey.org/wvs.jsp). Data on cultural tightness were retrieved from the OSF repository for ref[@Gelfand2021] (https://osf.io/47pe8/). The review data generated in this study are provided in Supplementary Data 1. All other datasets (e.g., for replications) were retrieved from tables and supplementary tables directly from papers cited in the main text[@Adamczyk2009;@Alesina2013;@Beck2003;@Beck2005;@Bockstette2002;@Easterly2003;@Easterly2007;@Fincher2008;@Gelfand2011;@Inglehart2000;@Knack1997;@Skidmore2002] - these datasets can be found in our GitHub repository[@github].

@@

All code to reproduce the statistical analyses in this manuscript can be found on GitHub[@github].

### 2023-08-08 manuscript.tex
final author changes

\linenumbers
\usepackage{csquotes}
\raggedbottom
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\AtBeginEnvironment{tablenotes}{\doublespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1,small}}
\nolinenumbers
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Cross-national analyses require additional controls to account for the non-independence of nations},
  pdfauthor={Scott Claessens1, Thanos Kyritsis1, \& Quentin D. Atkinson1,2},
  pdflang={en-EN},
  pdfkeywords={spatial non-independence; cultural non-independence; cross-national analyses; simulations; replications; reanalyses},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}

\title{Cross-national analyses require additional controls to account for the non-independence of nations}
\author{Scott Claessens\textsuperscript{1}, Thanos Kyritsis\textsuperscript{1}, \& Quentin D. Atkinson\textsuperscript{1,2}}
\date{}

@@

\authornote{Correspondence concerning this article should be addressed to Scott Claessens (\href{mailto:scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}}) and Quentin D. Atkinson (\href{mailto:q.atkinson@auckland.ac.nz}{\nolinkurl{q.atkinson@auckland.ac.nz}}), Floor 2, Building 302, 23 Symonds Street, Auckland, 1010, New Zealand. \newline \indent The authors made the following contributions. Scott Claessens: Conceptualization, Data curation, Formal analysis, Investigation, Software, Visualization, Writing - original draft, Writing - review \& editing; Thanos Kyritsis: Data curation, Writing - review \& editing; Quentin D. Atkinson: Conceptualization, Data curation, Funding acquisition, Supervision, Writing - review \& editing.}

\affiliation{\vspace{0.5cm}\textsuperscript{1} \footnotesize School of Psychology, University of Auckland, Auckland, New Zealand\\\textsuperscript{2} \footnotesize School of Anthropology and Museum Ethnography, University of Oxford, Oxford, United Kingdom}

@@

@@

Given that economic development and cultural values show evidence of geographic and cultural phylogenetic signal, have cross-national analyses sufficiently accounted for this non-independence? To assess this, we searched the published literature for articles that combined the search terms ``economic development'' or ``values'' with the search terms ``cross-national'', ``cross-cultural'', or ``cross-country''. We removed articles that did not report original research, were not relevant to economic development or cultural values, or did not report at least one cross-national analysis. We then retained the 100 articles (50 for economic development, 50 for cultural values) with the highest annual rate of citations (see Supplementary Data). For each of these highly-cited articles, we exhaustively recorded every cross-national analysis reported in the main text (n = 4,308), identifying in each case whether or not the analysis attempted to control for spatial, cultural, or any other form of non-independence between nations (see Methods for detailed search criteria and coding decisions).

@@

We exported two searches from Web of Science (\url{https://www.webofknowledge.com/}) on 27\textsuperscript{th} September 2021, restricting our searches to articles published between 1900 and 2018. The first search was for the terms ``economic development'' AND (``cross-national'' OR ``cross-cultural'' OR ``cross-country''), which returned 965 articles. The second search was for the terms ``values'' AND (``cross-national'' OR ``cross-cultural'' OR ``cross-country''), which returned 6806 articles. Once exported, we ordered the articles by descending number of citations per year since initial publication, using citation counts reported by Web of Science.

We then coded each article, in order, for inclusion in our review. Articles were only included if: (1) they were judged to be relevant to economic development or cultural values; (2) they were an original empirical research article; and (3) they contained at least one analysis with national-level outcome or predictor variables. We stopped when we had included 50 articles for the economic development review and 50 articles for the cultural values review.

@@

We coded common attempts to control for non-independence between nations. These included: (1) any higher-level control variables for spatial regional groupings (e.g.~continent fixed effects); (2) any geographic distance control variables (e.g.~distance between capital cities, distance from equator, latitude); (3) any control variables capturing shared cultural history (e.g.~former colony, legal origin fixed effects, linguistic history, cultural influence); and (4) any other control variables, tests, or approaches that were deemed as attempts to control for non-independence (e.g.~eigenvector filtering\textsuperscript{89}, controls for trade-weightings between nations, cross-sectional dependence tests\textsuperscript{90}, separate analyses for subsets of nations). These were coded by the first author.

@@

Models employing Conley standard errors either required latitude and longitude values or coordinates for genetic distances. To determine distance cutoffs, we employed an approach recommended in previous work\textsuperscript{91}: we fitted models with a range of feasible distance cutoffs and retained the model with the largest standard error for the slope parameter. These models were fitted using the conleyreg R package\textsuperscript{92}. Bayesian models were fitted using the brms R package\textsuperscript{81}. Our choice of priors was based on prior predictive simulation. All models converged normally (\(\hat{R}\) \textless{} 1.1). Across all model types and parameter combinations, we calculated the false positive rate as the proportion of models that estimated slopes with a two-tailed 95\% confidence / credible interval excluding zero when \(r = 0\). We calculated statistical power as the proportion of models that estimated slopes with a 95\% confidence / credible interval excluding zero when \(r > 0\). We calculated two-tailed 95\% bootstrap confidence intervals for these false positive rates and statistical power estimates with 1,000 bootstrap iterations.

@@

We fitted these models using the brms R package\textsuperscript{81}. Our choice of priors was based on prior predictive simulation. All models converged normally (\(\hat{R}\) \textless{} 1.1), though for some models we resorted to using approximate Gaussian processes\textsuperscript{93} to reach convergence. The assumptions of these models were met: residuals were approximately normally distributed, though this was not formally tested.

@@

All data and code are accessible on GitHub (\url{https://github.com/ScottClaessens/crossNationalCorrelations})\textsuperscript{94}. We used the targets R package\textsuperscript{95} to create a reproducible data analysis pipeline and the papaja R package\textsuperscript{96} to reproducibly generate the manuscript.

@@

All data can be found on GitHub (\url{https://github.com/ScottClaessens/crossNationalCorrelations}). Data on human development were retrieved from the United Nations Development Programme (\url{https://hdr.undp.org/en/content/download-data}). Data on GDP per capita, annual GDP per capita growth, and the Gini coefficient were retrieved from the World Bank (\url{https://data.worldbank.org/}). Data on traditional vs.~secular values and survival vs.~self-expression values were retrieved from the World Values Survey (\url{https://www.worldvaluessurvey.org/wvs.jsp}). Data on cultural tightness were retrieved from the OSF repository for Gelfand et al.~2021 (\url{https://osf.io/47pe8/}). The review data generated in this study are provided in the Supplementary Data file. All other datasets (e.g., for replications) were retrieved from tables and supplementary tables directly from papers cited in the main text\textsuperscript{13,14,16,55--63} - these datasets can be found in our GitHub repository.

@@

All code to reproduce the statistical analyses in this manuscript can be found on GitHub (\url{https://github.com/ScottClaessens/crossNationalCorrelations}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-hdi}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{\emph{Human development report}. \url{http://hdr.undp.org/en/composite/HDI}.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Ethnologue}{}}%
\CSLLeftMargin{87. }%
\CSLRightInline{\emph{Ethnologue: Languages of the world}. (SIL International, 2018).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Tiefelsdorf2007}{}}%
\CSLLeftMargin{89. }%
\CSLRightInline{Tiefelsdorf, M. \& Griffith, D. A. \href{https://doi.org/10.1068/a37378}{Semiparametric filtering of spatial autocorrelation: The eigenvector approach}. \emph{Environment and Planning A: Economy and Space} \textbf{39}, 1193--1221 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-DeHoyos2006}{}}%
\CSLLeftMargin{90. }%
\CSLRightInline{De Hoyos, R. E. \& Sarafidis, V. \href{https://doi.org/10.1177/1536867X0600600403}{Testing for cross-sectional dependence in panel-data models}. \emph{The Stata Journal} \textbf{6}, 482--496 (2006).}

\leavevmode\vadjust pre{\hypertarget{ref-Colella2019}{}}%
\CSLLeftMargin{91. }%
\CSLRightInline{Colella, F., Lalive, R., Sakalli, S. O. \& Thoenig, M. Inference with arbitrary clustering. \emph{IZA Discussion Paper No. 12584} (2019) doi:\href{https://doi.org/10.2139/ssrn.3449578}{10.2139/ssrn.3449578}.}

\leavevmode\vadjust pre{\hypertarget{ref-Duben2021}{}}%
\CSLLeftMargin{92. }%
\CSLRightInline{Düben, C. \emph{\href{https://CRAN.R-project.org/package=conleyreg}{{conleyreg}: Estimations using {C}onley standard errors}}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Solin2020}{}}%
\CSLLeftMargin{93. }%
\CSLRightInline{Solin, A. \& Särkkä, S. Hilbert space methods for reduced-rank {G}aussian process regression. \emph{Statistics and Computing} \textbf{30}, 419--446 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-github}{}}%
\CSLLeftMargin{94. }%
\CSLRightInline{Claessens, S., Kyritsis, T. \& Atkinson, Q. D. Cross-national analyses require additional controls to account for the non-independence of nations - ScottClaessens/crossNationalCorrelations: v1.0.0. (2023) doi:\href{https://doi.org/10.5281/zenodo.8128702}{10.5281/zenodo.8128702}.}

\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
\CSLLeftMargin{95. }%
\CSLRightInline{Landau, W. M. \href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}. \emph{Journal of Open Source Software} \textbf{6}, 2959 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Aust2020}{}}%
\CSLLeftMargin{96. }%
\CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Create} {APA} manuscripts with {R Markdown}}}. (2020).}

>>>>

\linenumbers
\usepackage{csquotes}
\raggedbottom
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\AtBeginEnvironment{tablenotes}{\doublespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1,small}}
\nolinenumbers
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Cross-national analyses require additional controls to account for the non-independence of nations},
  pdfauthor={Scott Claessens1*, Thanos Kyritsis1, \& Quentin D. Atkinson1,2*},
  pdflang={en-EN},
  pdfkeywords={spatial non-independence; cultural non-independence; cross-national analyses; simulations; replications; reanalyses},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}

\title{Cross-national analyses require additional controls to account for the non-independence of nations}
\author{Scott Claessens\textsuperscript{1*}, Thanos Kyritsis\textsuperscript{1}, \& Quentin D. Atkinson\textsuperscript{1,2*}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} \footnotesize School of Psychology, University of Auckland, Auckland, New Zealand\\\textsuperscript{2} \footnotesize School of Anthropology and Museum Ethnography, University of Oxford, Oxford, United Kingdom \newline *email: \href{mailto:scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}}; \href{mailto:q.atkinson@auckland.ac.nz}{\nolinkurl{q.atkinson@auckland.ac.nz}}}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

Given that economic development and cultural values show evidence of geographic and cultural phylogenetic signal, have cross-national analyses sufficiently accounted for this non-independence? To assess this, we searched the published literature for articles that combined the search terms ``economic development'' or ``values'' with the search terms ``cross-national'', ``cross-cultural'', or ``cross-country''. We removed articles that did not report original research, were not relevant to economic development or cultural values, or did not report at least one cross-national analysis. We then retained the 100 articles (50 for economic development, 50 for cultural values) with the highest annual rate of citations (see Supplementary Data 1). For each of these highly-cited articles, we exhaustively recorded every cross-national analysis reported in the main text (n = 4,308), identifying in each case whether or not the analysis attempted to control for spatial, cultural, or any other form of non-independence between nations (see Methods for detailed search criteria and coding decisions).

@@

We exported two searches from Web of Science (\url{https://www.webofknowledge.com/}) on 27\textsuperscript{th} September 2021, restricting our searches to articles published between 1900 and 2018. The first search was for the terms ``economic development'' AND (``cross-national'' OR ``cross-cultural'' OR ``cross-country''), which returned 965 articles. The second search was for the terms ``values'' AND (``cross-national'' OR ``cross-cultural'' OR ``cross-country''), which returned 6806 articles. As this was not a formal systematic literature review, we did not follow PRISMA\textsuperscript{89} guidelines for systematic literature reviews.

Once exported, we ordered the articles by descending number of citations per year since initial publication, using citation counts reported by Web of Science. We then coded each article, in order, for inclusion in our review. Articles were only included if: (1) they were judged to be relevant to economic development or cultural values; (2) they were an original empirical research article; and (3) they contained at least one analysis with national-level outcome or predictor variables. We stopped when we had included 50 articles for the economic development review and 50 articles for the cultural values review.

@@

We coded common attempts to control for non-independence between nations. These included: (1) any higher-level control variables for spatial regional groupings (e.g.~continent fixed effects); (2) any geographic distance control variables (e.g.~distance between capital cities, distance from equator, latitude); (3) any control variables capturing shared cultural history (e.g.~former colony, legal origin fixed effects, linguistic history, cultural influence); and (4) any other control variables, tests, or approaches that were deemed as attempts to control for non-independence (e.g.~eigenvector filtering\textsuperscript{90}, controls for trade-weightings between nations, cross-sectional dependence tests\textsuperscript{91}, separate analyses for subsets of nations). These were coded by the first author.

@@

Models employing Conley standard errors either required latitude and longitude values or coordinates for genetic distances. To determine distance cutoffs, we employed an approach recommended in previous work\textsuperscript{92}: we fitted models with a range of feasible distance cutoffs and retained the model with the largest standard error for the slope parameter. These models were fitted using the conleyreg R package\textsuperscript{93}. Bayesian models were fitted using the brms R package\textsuperscript{81}. Our choice of priors was based on prior predictive simulation. All models converged normally (\(\hat{R}\) \textless{} 1.1). Across all model types and parameter combinations, we calculated the false positive rate as the proportion of models that estimated slopes with a two-tailed 95\% confidence / credible interval excluding zero when \(r = 0\). We calculated statistical power as the proportion of models that estimated slopes with a 95\% confidence / credible interval excluding zero when \(r > 0\). We calculated two-tailed 95\% bootstrap confidence intervals for these false positive rates and statistical power estimates with 1,000 bootstrap iterations.

@@

We fitted these models using the brms R package\textsuperscript{81}. Our choice of priors was based on prior predictive simulation. All models converged normally (\(\hat{R}\) \textless{} 1.1), though for some models we resorted to using approximate Gaussian processes\textsuperscript{94} to reach convergence. The assumptions of these models were met: residuals were approximately normally distributed, though this was not formally tested.

@@

All data and code are accessible on GitHub\textsuperscript{95}. We used the targets R package\textsuperscript{96} to create a reproducible data analysis pipeline and the papaja R package\textsuperscript{97} to reproducibly generate the manuscript.

@@

All data to reproduce the statistical analyses in this manuscript can be found on GitHub\textsuperscript{95}. Data on human development were retrieved from the United Nations Development Programme (\url{https://hdr.undp.org/en/content/download-data}). Data on GDP per capita, annual GDP per capita growth, and the Gini coefficient were retrieved from the World Bank (\url{https://data.worldbank.org/}). Data on traditional vs.~secular values and survival vs.~self-expression values were retrieved from the World Values Survey (\url{https://www.worldvaluessurvey.org/wvs.jsp}). Data on cultural tightness were retrieved from the OSF repository for ref\textsuperscript{83} (\url{https://osf.io/47pe8/}). The review data generated in this study are provided in Supplementary Data 1. All other datasets (e.g., for replications) were retrieved from tables and supplementary tables directly from papers cited in the main text\textsuperscript{13,14,16,55--63} - these datasets can be found in our GitHub repository\textsuperscript{95}.

@@

All code to reproduce the statistical analyses in this manuscript can be found on GitHub\textsuperscript{95}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-hdi}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{United Nations Development Programme. \emph{Human development report}. \url{http://hdr.undp.org/en/composite/HDI} (2021).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Ethnologue}{}}%
\CSLLeftMargin{87. }%
\CSLRightInline{Eberhard, D. M., Simons, G. F. \& Fennig, C. D. \emph{\href{https://www.ethnologue.com/}{Ethnologue: Languages of the world}}. (SIL International, 2018).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Page2021}{}}%
\CSLLeftMargin{89. }%
\CSLRightInline{Page, M. J. \emph{et al.} \href{https://doi.org/10.1136/bmj.n71}{The {PRISMA} 2020 statement: An updated guideline for reporting systematic reviews}. \emph{BMJ} \textbf{372}, (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Tiefelsdorf2007}{}}%
\CSLLeftMargin{90. }%
\CSLRightInline{Tiefelsdorf, M. \& Griffith, D. A. \href{https://doi.org/10.1068/a37378}{Semiparametric filtering of spatial autocorrelation: The eigenvector approach}. \emph{Environment and Planning A: Economy and Space} \textbf{39}, 1193--1221 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-DeHoyos2006}{}}%
\CSLLeftMargin{91. }%
\CSLRightInline{De Hoyos, R. E. \& Sarafidis, V. \href{https://doi.org/10.1177/1536867X0600600403}{Testing for cross-sectional dependence in panel-data models}. \emph{The Stata Journal} \textbf{6}, 482--496 (2006).}

\leavevmode\vadjust pre{\hypertarget{ref-Colella2019}{}}%
\CSLLeftMargin{92. }%
\CSLRightInline{Colella, F., Lalive, R., Sakalli, S. O. \& Thoenig, M. Inference with arbitrary clustering. \emph{IZA Discussion Paper No. 12584} (2019) doi:\href{https://doi.org/10.2139/ssrn.3449578}{10.2139/ssrn.3449578}.}

\leavevmode\vadjust pre{\hypertarget{ref-Duben2021}{}}%
\CSLLeftMargin{93. }%
\CSLRightInline{Düben, C. \emph{\href{https://CRAN.R-project.org/package=conleyreg}{{conleyreg}: Estimations using {C}onley standard errors}}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Solin2020}{}}%
\CSLLeftMargin{94. }%
\CSLRightInline{Solin, A. \& Särkkä, S. Hilbert space methods for reduced-rank {G}aussian process regression. \emph{Statistics and Computing} \textbf{30}, 419--446 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-github}{}}%
\CSLLeftMargin{95. }%
\CSLRightInline{Claessens, S., Kyritsis, T. \& Atkinson, Q. D. Cross-national analyses require additional controls to account for the non-independence of nations - ScottClaessens/crossNationalCorrelations: v1.0.0. (2023) doi:\href{https://doi.org/10.5281/zenodo.8128702}{10.5281/zenodo.8128702}.}

\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
\CSLLeftMargin{96. }%
\CSLRightInline{Landau, W. M. \href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}. \emph{Journal of Open Source Software} \textbf{6}, 2959 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Aust2020}{}}%
\CSLLeftMargin{97. }%
\CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Create} {APA} manuscripts with {R Markdown}}}. (2020).}
